\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}

\title{CODA --- Suggested Revisions}
\date{}

\begin{document}
\maketitle

\section*{Abstract}

\subsection*{Architecture Description (Lines 22--26)}

\textbf{Original:}
\begin{quote}
CODA's architecture combines a visual encoder with a causal Mamba state-space audio encoder.
Candidate positions are scored using audio-conditioned modulation and cross-attention, and decoded
using beam search with learned transition penalties.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
CODA combines a CNN visual backbone with a causal Mamba audio encoder.
At each frame, visual features of candidate regions are extracted and modulated by audio context
via FiLM conditioning and cross-attention over recent audio history.
The resulting scores are decoded over time using beam search with learned temporal transition priors.
\end{quote}

\textbf{Rationale:}
\begin{itemize}
    \item Specifies ``CNN visual backbone'' rather than the vague ``visual encoder'', giving the two encoders symmetric descriptive weight.
    \item Separates the encode $\to$ score $\to$ decode logic into three sentences with a clear causal chain.
    \item Distinguishes FiLM (frame-level global conditioning) and cross-attention (fine-grained temporal attention) as sequential rather than parallel operations.
    \item Adds ``temporal'' to ``transition priors'' to clarify that the learned penalties encode smoothness over time.
\end{itemize}


\section*{Introduction}

\subsection*{Item 2: ``recently emerged'' (Line 43)}

\textbf{Original:}
\begin{quote}
Image-based score following has recently emerged by working directly on sheet images.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
Image-based score following has emerged over the past decade by working directly on sheet images.
\end{quote}

\textbf{Rationale:}
``Recently'' is imprecise given that the earliest image-based work dates to 2016. ``Over the past decade'' is factually accurate while still conveying that the field is younger than symbolic score following, which has a history of several decades.

\subsection*{Item 3: Two senses of ``recovery'' (Lines 48--50)}

\textbf{Original:}
\begin{quote}
Reinforcement-learning methods widened the view to score strips but still operated on narrow windows, making recovery difficult when the agent drifted off track [7, 8].
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
Reinforcement-learning methods widened the view to score strips but still operated on narrow windows, making re-engagement difficult when the agent drifted off track [7, 8].
\end{quote}

\textbf{Rationale:}
The word ``recovery'' appears twice in the Introduction with different meanings: once for tracking drift (here) and once for jump recovery after a score discontinuity. Replacing ``recovery'' with ``re-engagement'' in this sentence removes the ambiguity without requiring any additional explanation.

\subsection*{Item 4: Contribution bullet alignment with Method (Lines 56--60)}

\textbf{Original:}
\begin{quote}
A cascaded selection formulation that enforces geometric consistency across system, bar, and note predictions while narrowing the search space at each stage.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
A cascaded selection-and-regression formulation that enforces geometric consistency across system, bar, and note predictions while narrowing the search space at each stage.
\end{quote}

\textbf{Rationale:}
In Section 3, the system and bar stages are selection tasks (classification over known candidates) while the note stage is a continuous regression of bar-local coordinates. Framing all three stages as ``selection'' in the contribution list blurs the distinction between classification and regression and does not match the Method section, where the note head is introduced as a sigmoid regressor. Replacing ``selection'' with ``selection-and-regression'' aligns the Introduction with the Method and pre-empts reader confusion when they reach Section 3.3.

\subsection*{Item 6: ``detection is unnecessary'' missing premise (Lines 73--80)}

\textbf{Original:}
\begin{quote}
However, in music performances, the score is static, and all candidate positions are known in advance. Detection is therefore unnecessary. The real task is to select which of the known candidates is currently being played.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
However, in music performances, the score is static, and all candidate positions are known in advance. Detection is therefore unnecessary. The real task is to select which of the known candidates is currently being played, a formulation that is feasible whenever score layout information is available.
\end{quote}

\textbf{Rationale:}
The claim that detection is unnecessary rests on the assumption that layout metadata (system and bar bounding boxes) is available for the score page. This premise is stated in Section 3.1 but not in the Introduction. Adding the qualifying clause makes the argument honest and pre-empts reviewer questions about cases where layout information is absent.

\subsection*{Item 7: Benchmark contribution separated into its own bullet (Lines 109--112)}

\textbf{Original:}
\begin{quote}
A silence-driven jump recovery mechanism for arbitrary score discontinuities, evaluated on a repeat-aware jump test benchmark that we contribute for the MSMD test set.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
A silence-driven jump recovery mechanism for arbitrary score discontinuities, including repeats, D.C., and coda jumps, without requiring prior knowledge of the score's repeat structure.

A repeat-aware jump test benchmark with manually annotated repeat structures for all 94 pieces in the MSMD test set, providing the first standardized evaluation protocol for discontinuity handling in image-based score following.
\end{quote}

\textbf{Rationale:}
The benchmark is an independent contribution that required substantial manual annotation effort. Merging it into the same bullet as the recovery mechanism undersells its value. Separating them gives each contribution its own visible presence in the list.

\subsection*{Item 8: Paragraph 4 expansion to give jump recovery appropriate weight (Lines 81--85)}

\textbf{Original:}
\begin{quote}
Additionally, existing image-based methods lack mechanisms to recover from score discontinuities such as repeats, D.C., or coda jumps, even though such events are common in practice and have long been addressed in symbolic score following [5, 11, 12].
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
Additionally, existing image-based methods lack mechanisms to recover from score discontinuities such as repeats, D.C., or coda jumps, even though such events are common in practice and have long been addressed in symbolic score following [5, 11, 12]. In our analysis of the MSMD test set, 66 out of 94 pieces contain written repeat structures, producing 131 jumps in standard performance order. Surprisingly, no existing real-time image-based score following method includes an explicit mechanism for handling such events during online tracking.
\end{quote}

\textbf{Rationale:}
The current single sentence gives jump recovery far less introductory weight than the cascaded selection problem, despite both being listed as major contributions. Adding two sentences with a concrete statistic from the benchmark and a direct statement of the gap in the literature raises the perceived importance of this contribution to match its presence in the paper.


\section*{Related Work}

\subsection*{RW Item 3: Emphasize Nakamura's silent breaks observation (Lines 125--128)}

\textbf{Original:}
\begin{quote}
Nakamura et al. [5] modeled repeats and skips with an explicit transition structure and observed that the majority of real-world score jumps are preceded by short silent breaks.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
Nakamura et al. [5] modeled repeats and skips with an explicit transition structure. Their analysis further revealed that the majority of real-world score jumps are preceded by short silent breaks, an observation that motivates the jump recovery design in Section 3.6.
\end{quote}

\textbf{Rationale:}
This observation is the empirical foundation for CODA's entire break mode mechanism. In the original text, it is buried in the second half of a compound sentence and easy to overlook. Splitting it into its own sentence and adding a forward reference to Section 3.6 gives the observation standalone visibility and lets the reader know it will be used later, without over-explaining.

\subsection*{RW Item 4: Reorder Section 2.1 for narrative coherence (Lines 115--137)}

\textbf{Original order:}
\begin{enumerate}
    \item Online DTW (Dixon [3])
    \item Probabilistic state-space models (Cont [4], Arzt and Widmer [13])
    \item Particle filters (Korzeniowski et al. [14])
    \item Repeats and skips (Nakamura et al. [5])
    \item Tempo tracking (Jiang and Raphael [15])
    \item AMT front end (Peter et al. [16])
    \item Evaluation framework (Matchmaker [12])
\end{enumerate}

\textbf{Suggested order:}
\begin{enumerate}
    \item Online DTW (Dixon [3])
    \item Probabilistic state-space models (Cont [4], Arzt and Widmer [13])
    \item Particle filters (Korzeniowski et al. [14])
    \item Tempo tracking (Jiang and Raphael [15])
    \item Repeats and skips (Nakamura et al. [5])
    \item AMT front end (Peter et al. [16])
    \item Evaluation framework (Matchmaker [12])
\end{enumerate}

\textbf{Rationale:}
In the original order, Jiang and Raphael (tempo tracking) appears after Nakamura (repeats and skips), which breaks the thematic flow. Items 1 through 4 in the suggested order all address improving tracking under normal performance conditions (tempo, rests, expressive variation). Item 5 then shifts to structural discontinuities, forming a natural thematic transition toward Section 2.3. Items 6 and 7 close with the most recent method and the evaluation framework.

\subsection*{RW Item 6: Replace ``systematized'' (Line 134)}

\textbf{Original:}
\begin{quote}
Matchmaker [12] has systematized evaluation of symbolic methods into an open-source benchmarking framework, though it does not cover image-based trackers.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
Matchmaker [12] provides a systematic evaluation framework for symbolic methods, though it does not cover image-based trackers.
\end{quote}

\textbf{Rationale:}
``Systematized'' is uncommon and slightly awkward. ``Provides a systematic evaluation framework'' conveys the same meaning in more natural academic English.

\subsection*{RW Item 8: Precision of CYOLO temporal independence claim (Lines 151--153)}

\textbf{Original:}
\begin{quote}
However, the three heads predict in parallel without cross-level constraints, each frame is decoded independently of the previous one, and no recovery mechanism exists for when tracking is lost.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
However, the three heads predict in parallel without cross-level constraints, predictions at each frame are decoded without temporal consistency constraints across frames, and no recovery mechanism exists for when tracking is lost.
\end{quote}

\textbf{Rationale:}
CYOLO uses an LSTM to process the audio sequence, which does provide temporal context at the audio encoding level. The original phrasing ``each frame is decoded independently of the previous one'' could be read as claiming that CYOLO has no temporal memory at all, which is inaccurate. The revised phrasing makes the criticism precise: what CYOLO lacks is not temporal audio context but temporal consistency constraints at the prediction output level. That is, the predicted system, bar, and note at frame $t$ are not constrained by the predictions at frame $t{-}1$. This is the specific gap that CODA's beam search and learned temporal priors address.

\section*{Method}

\subsection*{Item 1: ``inherently'' $\to$ ``by construction'' (Line 96)}

\textbf{Original:}
\begin{quote}
This cascaded factorization inherently enforces valid geometric structure: the predicted bar always lies within the predicted system, and the predicted note always lies within the predicted bar.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
This cascaded factorization enforces valid geometric structure by construction: the predicted bar always lies within the predicted system, and the predicted note always lies within the predicted bar.
\end{quote}

\textbf{Rationale:}
``Inherently'' suggests an intrinsic property without specifying its source. The geometric guarantee actually comes from restricting each stage's candidate set based on the previous stage's prediction, which is an architectural design choice. ``By construction'' names the source of the guarantee more precisely and contrasts more sharply with the criticism of CYOLO in Section 2.2, where the model is said to ``implicitly'' learn structural consistency. The revision also pre-empts reviewer questions about whether ``inherently'' refers to a mathematical property or an implementation choice.

\subsection*{Item 2: Align Figure~1 caption with Section 3.2 stream order (Line 78 caption and Line 101)}

\textit{Status: Adopted (change the caption to lead with audio).}

\textbf{Current state:}
\begin{itemize}
    \item Figure~1 caption (Line 78) introduces the two streams in the order ``CNN visual backbone and \ldots Mamba audio encoder'' (visual first).
    \item Section~3.2 body text (Line 101) introduces them as ``audio and visual'' (audio first), and the two paragraphs that follow are ordered audio paragraph $\to$ visual paragraph.
\end{itemize}

\textbf{Suggested revision:}
Change the Figure~1 caption to lead with the audio stream so that it matches the body text:
\begin{quote}
Overview of the CODA architecture. A causal Mamba audio encoder and a shared CNN visual backbone feed into three cascaded stages: system selection, bar selection, and note localization. Beam search with learned temporal priors decodes the cascade over time.
\end{quote}

\textbf{Rationale:}
Small cross-reference inconsistencies between body text and figure captions are a low-stakes issue individually but accumulate when reviewers scan both artifacts. Aligning the order in the caption with the body text costs one line and removes a latent source of reading friction. Changing the caption (rather than the body) is strictly less invasive because the body has two full paragraphs in the audio-first order that would otherwise need to be reshuffled.

\subsection*{Item 3: Remove ``global'' from the description of $z_t$ (Line 103 and Line 124)}

\textit{Status: Adopted (delete ``global'' in both places).}

\textbf{Original (Line 103):}
\begin{quote}
A two-layer causal Mamba encoder processes each frame, producing a global conditioning vector $z_t$ and a buffer of recent hidden states $H_t$.
\end{quote}

\textbf{Original (Line 124):}
\begin{quote}
The extracted features $f_r$ are then modulated by the global audio vector $z_t$ via Feature-wise Linear Modulation (FiLM) \ldots
\end{quote}

\textbf{Suggested revision:}
Delete ``global'' in both places:
\begin{quote}
(Line 103) \ldots producing a conditioning vector $z_t$ and \ldots\\
(Line 124) \ldots modulated by the audio vector $z_t$ via FiLM \ldots
\end{quote}

\textbf{Rationale:}
The word ``global'' is not factually wrong --- depending on which convention a reader brings in, it can be read as ``whole-history-aware'' (reasonable, since Mamba's recurrent state accumulates all past audio into $z_t$) or as ``applied spatially globally to the full visual feature map via FiLM'' (also reasonable, describing how $z_t$ is used downstream). The problem is that a third reading, ``pooled over time,'' is equally natural in deep-learning usage (cf.\ global average pooling), and this reading is inconsistent with the implementation: $z_t$ is not time-pooled but is produced per frame from the current Mamba hidden state. Dropping ``global'' removes the ambiguous reading at no cost; the following sentence (``$z_t$ summarizes the audio context up to frame $t$'') already conveys the intended whole-history-aware meaning.

\subsection*{Item 4: Make both audio-history mechanisms explicit in Section 3.2 (Line 103)}

\textit{Status: Adopted.}

\textbf{Original (Line 103):}
\begin{quote}
A two-layer causal Mamba encoder processes each frame, producing a global conditioning vector $z_t$ and a buffer of recent hidden states $H_t$. $z_t$ summarizes the audio context up to frame~$t$, while $H_t$ serves as the key and value source for cross-attention (Eq.~\ref{eq:crossattn}).
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
A two-layer causal Mamba encoder processes each frame. Its recurrent state compactly accumulates the entire audio history up to frame~$t$, yielding a conditioning vector $z_t$. In parallel, we maintain a sliding window $H_t$ of the most recent $L$ per-frame outputs. $z_t$ provides global conditioning for the visual feature map (Eq.~\ref{eq:film}), while $H_t$ serves as the key and value source for cross-attention (Eq.~\ref{eq:crossattn}).
\end{quote}

\textbf{Rationale:}
The original wording ``producing a global conditioning vector $z_t$ and a buffer of recent hidden states $H_t$'' conflates two distinct audio-history mechanisms and slightly misattributes the buffer to the encoder. CODA actually uses two complementary stores:
\begin{itemize}
    \item \emph{Mamba's recurrent state} (O(1) memory, fixed size) compactly accumulates all past audio into a single vector. This is the source of $z_t$, and is the reason $z_t$ can ``summarize the audio context up to frame~$t$'' without any explicit buffering.
    \item \emph{A sliding window of the most recent $L$ per-frame Mamba outputs} (O($L$) memory, $L = 64$ frames $\approx 3.2$\,s at 20\,fps). This is $H_t$, maintained externally to the encoder (a \texttt{deque} in the streaming inference loop; an internal truncation inside the cross-attention head at training time). It preserves per-frame resolution so that cross-attention can do fine-grained temporal alignment.
\end{itemize}
Making both mechanisms explicit clarifies how a single vector $z_t$ can encode arbitrarily long history (via the recurrent state) and why a separate windowed $H_t$ is still needed (for per-frame cross-attention). It also fixes the attribution: the windowing of $H_t$ is not performed inside the encoder. The revised sentence also integrates the usage description into the same paragraph, letting the third sentence be dropped or shortened.

\subsection*{Item 5: Name the FiLM condition source in Section 3.2 (Line 105)}

\textit{Status: Adopted (if space permits).}

\textbf{Original:}
\begin{quote}
The score page image is processed by a CNN backbone with FiLM conditioning at deeper stages.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
The score page image is processed by a CNN backbone with FiLM conditioning at deeper stages, driven by the audio conditioning vector $z_t$.
\end{quote}

\textbf{Rationale:}
The current sentence introduces FiLM without naming what the modulation is conditioned on. A first-time reader must hold the question in mind until Section~3.3 (Eq.~\ref{eq:film}) to learn that $z_t$ is the conditioning input. Naming $z_t$ here costs a short clause and forms an explicit bridge between the audio and visual streams at the architectural level. This is a low-severity readability fix, worth adopting only if column space allows.

\subsection*{Item 6: Drop ``single'' before ``stride-8 feature map'' (Line 105)}

\textit{Status: Adopted.}

\textbf{Original:}
\begin{quote}
\ldots further processed by a Feature Pyramid Network (FPN) that produces a single stride-8 feature map $F$.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
\ldots further processed by a Feature Pyramid Network (FPN) that produces a stride-8 feature map $F$.
\end{quote}

\textbf{Rationale:}
The CNN backbone actually produces both a stride-8 feature map (P3) and a stride-16 feature map (P4); the design choice is to use only P3 for all downstream cascade stages. The word ``single'' reads as a statement about the FPN architecture (as if the FPN has one output), which would be at odds with the standard definition of an FPN. A reviewer familiar with object-detection architectures may flag this. Dropping ``single'' makes the sentence truthful without adding length. A slightly more explicit alternative is ``we use the finest (stride-8) FPN output as $F$.''

\subsection*{Item 7: Drop ``in the selection process'' (Line 105)}

\textit{Status: Adopted.}

\textbf{Original:}
\begin{quote}
This feature map is shared across all three cascade stages in the selection process.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
This feature map is shared across all three cascade stages.
\end{quote}

\textbf{Rationale:}
The note stage is a continuous regression, not a selection over candidates. Calling all three cascade stages part of ``the selection process'' repeats the same terminology mismatch addressed by Introduction Item~4 (contribution-bullet alignment). Deleting ``in the selection process'' removes the mismatch and shortens the sentence. This revision is paired with Introduction Item~4 for consistency.

\subsection*{Item 8: Weaken ``share the same processing pipeline'' (Line 109)}

\textit{Status: Adopted.}

\textbf{Original:}
\begin{quote}
All three stages share the same processing pipeline, which we describe below.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
All three stages share a common processing pipeline, with stage-specific variations detailed below.
\end{quote}

\textbf{Rationale:}
The note stage actually omits cross-attention (see Line 138: ``The note stage uses only Eqs.~\ref{eq:roi}--\ref{eq:conv}''), so saying ``the same'' overstates the commonality and is internally inconsistent with the paragraph three lines later. Softening ``the same'' to ``a common \ldots (with stage-specific variations)'' preserves the useful scaffolding while remaining accurate.

\subsection*{Item 9: Remove redundant $H_t$ definition in Section 3.3 (Line 118)}

\textit{Status: Adopted. Applies only after Method Item~4 lands.}

\textbf{Original (Line 118):}
\begin{quote}
Let $H_t = [h_{t-L+1}, \ldots, h_t] \in \mathbb{R}^{L \times d}$ denote the buffer of the most recent~$L$ Mamba hidden states, where $d$ is the hidden dimension of the Mamba encoder.
\end{quote}

\textbf{Suggested revision:}
Shorten to a recall pointer:
\begin{quote}
Recall from Section~\ref{sec:method} (Model Architecture) that $H_t \in \mathbb{R}^{L \times d}$ is the sliding window of the most recent $L$ Mamba hidden states, with $d$ the hidden dimension of the encoder.
\end{quote}
Alternatively, delete the sentence entirely and introduce the notation $L$, $d$ at first use within the Eq.~\ref{eq:crossattn} description.

\textbf{Rationale:}
Method Item~4 (Model Architecture) introduces $H_t$ in Section~3.2 with the sliding-window semantics. Keeping a second full definition here duplicates the content. A recall pointer preserves reading flow for readers skimming directly into Section~3.3 and avoids any ``wait, was this already defined?'' friction.

\subsection*{Item 10: Move ``(i.e., at one-eighth the spatial resolution of the input)'' to first mention of stride (Line 105 vs.\ Line 120)}

\textit{Status: Adopted.}

\textbf{Original (Line 105, Section 3.2):}
\begin{quote}
\ldots further processed by a Feature Pyramid Network (FPN) that produces a stride-8 feature map $F$.
\end{quote}

\textbf{Original (Line 120, Section 3.3):}
\begin{quote}
First, Region of Interest (ROI) Align \cite{he2017mask} extracts a fixed-size feature patch from the stride-8 feature map (i.e., at one-eighth the spatial resolution of the input):
\end{quote}

\textbf{Suggested revision:}
Move the parenthetical gloss to the first mention of stride:
\begin{quote}
(Line 105, Section 3.2) \ldots produces a stride-8 feature map $F$ (i.e., at one-eighth the spatial resolution of the input).\\
(Line 120, Section 3.3) First, Region of Interest (ROI) Align \cite{he2017mask} extracts a fixed-size feature patch from the stride-8 feature map:
\end{quote}

\textbf{Rationale:}
The parenthetical explains what ``stride-8'' means. Placing this gloss where the term is first introduced (Section~3.2) is more pedagogically coherent than repeating it on second use in Section~3.3. This also shortens Section~3.3 slightly, which helps absorb the small length increases from Items~4, 5, and 9.

\subsection*{Item 11: Rename the attention-scaling constant in Eq.~\ref{eq:crossattn} to avoid reusing $d$ (Line 118 and Line 134)}

\textit{Status: Adopted in principle; final choice of symbol ($C$ vs.\ $d_k$) to be confirmed with Ruogu.}

\textbf{Original (Line 118):}
\begin{quote}
\ldots where $d$ is the hidden dimension of the Mamba encoder.
\end{quote}

\textbf{Original (Line 134, Eq.~\ref{eq:crossattn}):}
\begin{equation*}
\bar{f}_r = \mathrm{softmax}\!\left(\frac{\mathrm{flat}(\hat{f}_r)\,(W_a H_t)^\top}{\sqrt{d}}\right) W_a H_t
\end{equation*}

\textbf{The problem:}
As defined on Line 118, $d$ is the Mamba hidden dimension (64 in the implementation). The scaling factor $\sqrt{d}$ in scaled dot-product attention, however, should be the key dimension \emph{after} the projection $W_a$: $W_a$ projects the 64-dimensional $H_t$ into the $C$-dimensional attention space that matches the convolved visual features (128 channels in the implementation). Reusing the same symbol $d$ for two different dimensions is dimensionally inconsistent.

\textbf{Suggested revision (option A, simpler):}
Replace $\sqrt{d}$ in Eq.~\ref{eq:crossattn} with $\sqrt{C}$, and amend the description below Eq.~\ref{eq:crossattn}:
\begin{quote}
$\bar{f}_r = \mathrm{softmax}\!\left(\dfrac{\mathrm{flat}(\hat{f}_r)\,(W_a H_t)^\top}{\sqrt{C}}\right) W_a H_t$,\\[2pt]
where $W_a$ is a learned linear projection onto the $C$-dimensional attention space shared with $\hat{f}_r$.
\end{quote}

\textbf{Suggested revision (option B, more standard):}
Write $\sqrt{d_k}$ and add a definition: ``$d_k$ denotes the per-head key dimension.'' This reads as textbook scaled dot-product attention notation but introduces a new symbol that might encourage a reviewer to ask about the multi-head decomposition (which the paper's single-head presentation otherwise glosses over).

\textbf{Rationale:}
A careful reviewer comparing the dimensions of $\mathrm{flat}(\hat{f}_r)$ (in the $C$-dimensional feature space) and $W_a H_t$ (produced by projecting from $d$ to $C$) will immediately notice that the current $\sqrt{d}$ is dimensionally wrong. Option~A resolves the inconsistency with one symbol change and does not introduce any new notation the paper does not already use. Option~B is closer to common attention-paper notation but adds bookkeeping.

\subsection*{Item 12: State softmax normalization explicitly (Line 138)}

\textit{Status: Adopted.}

\textbf{Original:}
\begin{quote}
The system stage applies Eqs.~\ref{eq:roi}--\ref{eq:crossattn} to every system candidate on the page, producing~$\log p(s_t \mid h_t)$ via adaptive average pooling and a linear classifier.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
The system stage applies Eqs.~\ref{eq:roi}--\ref{eq:crossattn} to every system candidate on the page, producing~$\log p(s_t \mid h_t)$ via adaptive average pooling and a linear classifier followed by softmax normalization.
\end{quote}

\textbf{Rationale:}
A linear classifier produces unnormalized logits, not log-probabilities. The softmax over candidates is what turns these into $\log p(\cdot)$. Stating the softmax step explicitly removes a small notational gap between ``linear classifier'' (logit-producing) and the probabilistic output $\log p(s_t \mid h_t)$.

\subsection*{Item 13: Replace ``because the search space is small enough'' with ``at this stage'' (Line 138)}

\textit{Status: Adopted.}

\textbf{Original:}
\begin{quote}
The note stage uses only Eqs.~\ref{eq:roi}--\ref{eq:conv} (no cross-attention because the search space is small enough) on the selected bar and regresses bar-local coordinates $u_t = (c_x, c_y) \in [0,1]^2$ via sigmoid activation.
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
The note stage uses only Eqs.~\ref{eq:roi}--\ref{eq:conv} (no cross-attention at this stage) on the selected bar and regresses bar-local coordinates $u_t = (c_x, c_y) \in [0,1]^2$ via sigmoid activation.
\end{quote}

\textbf{Rationale:}
``Because the search space is small enough'' is a vague justification that invites the reviewer question ``how small is small enough?'' The note stage's actual design motivation (only one ROI remains; cross-temporal matching is not needed for a regression target within a bar) can be documented in Implementation details or elaborated in an ablation if space permits. Replacing the phrase with ``at this stage'' states the architectural fact without making a claim that would need defending.

\subsection*{Item 14: Remove forward declaration of $f_r$ (Lines 118 and 120)}

\textit{Status: Adopted.}

\textbf{Original (Line 118, last sentence):}
\begin{quote}
\ldots For each candidate region~$r$ (a system or bar bounding box from the score layout metadata), let $f_r$ denote the extracted visual features for~$r$. The pipeline proceeds as follows.
\end{quote}

\textbf{Original (Line 120, Eq.~\ref{eq:roi} introduction):}
\begin{quote}
First, Region of Interest (ROI) Align \cite{he2017mask} extracts a fixed-size feature patch from the stride-8 feature map:
\end{quote}

\textbf{Suggested revision:}
Delete ``let $f_r$ denote the extracted visual features for~$r$'' from Line 118, and introduce $f_r$ at the point of use in Line 120:
\begin{quote}
(Line 118) \ldots For each candidate region~$r$ (a system or bar bounding box from the score layout metadata), the pipeline proceeds as follows.\\[4pt]
(Line 120) First, Region of Interest (ROI) Align \cite{he2017mask} extracts a fixed-size feature patch $f_r$ from the stride-8 feature map:
\end{quote}

\textbf{Rationale:}
The original structure forward-declares $f_r$ (``let $f_r$ denote \ldots'') before defining how it is extracted, then defines extraction via Eq.~\ref{eq:roi} one sentence later. Introducing $f_r$ directly at the point of extraction eliminates the forward declaration, saves one sentence, and keeps the prose in the paper's prevailing third-person, impersonal voice (avoiding first-person alternatives such as ``we extract $f_r$ \ldots'').


\section*{Experiments}

\subsection*{Item 1: Clarify layout metadata source (Line 189, Section 4.1.1)}

\textbf{Original:}
\begin{quote}
Training and evaluation are both based on the MSMD dataset [18], using the preprocessed version provided by Henkel and Widmer [10], in which each piece is stored as a score image with per-note coordinate annotations and a paired synthesized audio file (22,050 Hz).
\end{quote}

\textbf{Suggested revision:}
\begin{quote}
Training and evaluation are both based on the MSMD dataset [18], using the preprocessed version provided by Henkel and Widmer [10], in which each piece is stored as a score image with per-note coordinate annotations and per-system and per-bar bounding box annotations, paired with a synthesized audio file (22,050 Hz).
\end{quote}

\textbf{Rationale:}
Section 3.1 and Section 3.3 refer to ``layout metadata'' (system and bar bounding boxes) as a precondition for CODA's selection formulation, but the Dataset description currently only mentions per-note coordinate annotations. Without this addition, readers may assume the system and bar boxes come from an external OMR module or from proprietary annotations, which would raise unwarranted concerns about the method's applicability. Spelling out that the boxes are part of the MSMD distribution closes this gap and matches the actual preconditions of the method.

\subsection*{Item 2: Peter et al. not directly comparable (Section 4.1.3 Baselines)}

\textit{Note: originally recorded as ``RW Item 5'' during the Related Work pass; relocated here now that the Experiments section has its own heading.}

\textbf{Suggested addition at the end of Section 4.1.3:}
\begin{quote}
Methods that rely on automatic music transcription as a front end, such as Peter et al. [16], are not directly comparable because they depend on symbolic-level intermediate representations rather than operating on sheet images.
\end{quote}

\textbf{Rationale:}
Peter et al. [16] is cited in Section 2.1 as a recent strong result in symbolic score following. Reviewers familiar with this work may wonder why it does not appear in Table 1. A brief sentence in the Baselines subsection clarifies that the comparison is limited to image-based methods and that transcription-based approaches fall outside this scope.

\end{document}

